Binary companions of red giant stars with APOGEE DR14

### 2018-02-23 paper/1-catalog/twoface-catalog.tex
Math to appendix

\subsection{Individual-system posterior samplings}
\label{sec:initsampling}

@@

\todo{Move math to appendix since we cite relevant papers that show how?}
In detail, we maximize the marginal likelihood of the population-level
parameters $\bs{\alpha} = (\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given
vector $\bs{\alpha}$ over the value of the default prior at the previously
assumed values, $\bs{\alpha}_0 = (\mu_{y,0}, \sigma_{y,0})$ (see
\sectionname~\ref{sec:initsampling}).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters
(\citealt{Hogg:2010,Foreman-Mackey:2014}); we describe how to compute the
marginal likelihood in detail below.

@@

>>>>

\subsection{Individual-system posterior samplings}
\label{sec:samplings}

@@

In detail, we maximize the marginal likelihood of the population-level
parameters $(\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given,
new set of parameters $(\mu_y, \sigma_y)$ over the value of the default prior at
the previously assumed values, $(\mu_{y,0}, \sigma_{y,0})$ (see above).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters to infer population-level parameters
(\citealt{Hogg:2010,Foreman-Mackey:2014}); we describe how to compute the
marginal likelihood in detail in \sectionname~\ref{sec:hierarch}.

@@

\appendix
\section{Hierarchical inference of the excess variance parameter}
\label{sec:hierarch}
